Out-of-Sample Comparisons of Overfit Models

### 2014-02-25 paper.tex
Edit assumptions

\begin{asmp}\label{asmp-3}
  The loss function $L$ is continuous, has finite left and right
  derivatives almost everywhere, and $L(0) = 0$.  There is a constant
  $B_L$ and a function $L'$ that bounds the left and right derivative
  of $L$ such that $\|D_t\|_\rho \leq B_L$; $\|D_t^*\|_\rho \leq B_L$
  for all $t$, where
  \begin{equation*}
    D_t^* = L(y^* - x_1^{*\prime}\hat\theta_{1t})
    - L(y^* - x_2^{*\prime}\hat\theta_{2t})
  \end{equation*}
  and $(y^*, x_1^*, x_2^*)$ equals $(y_t, x_{1t}, x_{2t})$ in
  distribution but is independent of $\mathcal{F}_T$ ($\rho$ is defined
  in Assumption~\ref{asmp-1}); and
  \begin{equation*}
    \| L'(y^* - x_{i}^{*\prime}
    (\alpha \hat{\theta}_{iR} + (1-\alpha) \hat{\theta}_{iT})) \|_2
    \leq B_L
  \end{equation*}
  for any $\alpha \in [0,1]$.
\end{asmp}

This third assumption establishes basic moment and smoothness
conditions for the \oos\ loss and forecasts.  The differentiability
condition is weak and allows the loss function itself to be
non-differentiable or even discontinuous; for example, absolute error
and many asymmetric loss functions satisfy this assumption.

\begin{asmp} \label{asmp-4} $P, R, Q \to\infty$ and $P^2/T \to 0$ as
  $T \to \infty$.
\end{asmp}

The requirements that $P$ and $R$ grow with $T$ are common.  Parts of
the assumption are new, in particular the requirement that $P^2/T \to
0$.  See Lemma \ref{res-convergence} for a discussion of its
implications.  In practical terms, this assumption requires that the
test sample be large and that the training sample be much larger, by
enough that including or excluding the test sample does not affect the
estimates of $\theta_1$ or $\theta_2$ very much.

>>>>

The next assumption establishes moment conditions for the \oos\ loss
process and smoothness conditions for the loss function itself. The
moment conditions are standard and apply to $D_t$, and the smoothness
conditions are relatively weak.

\begin{asmp}\label{asmp-3}
  The loss function $L$ is continuous, has finite left and right
  derivatives, and $L(0) = 0$.  There is a constant $B_L$ and a
  function $L'$ that bounds the left and right derivative of $L$ at
  every point such that $\|D_t\|_\rho \leq B_L$; $\|D_t^*\|_\rho \leq
  B_L$ for all $t$, where
  \begin{equation*}
    D_t^* = L(y^* - x_1^{*\prime}\hat\theta_{1t})
    - L(y^* - x_2^{*\prime}\hat\theta_{2t})
  \end{equation*}
  and $(y^*, x_1^*, x_2^*)$ equals $(y_t, x_{1t}, x_{2t})$ in
  distribution but is independent of $\mathcal{F}_T$ ($\rho$ is defined
  in Assumption~\ref{asmp-1}); and
  \begin{equation*}
    \| L'(y^* - x_{i}^{*\prime}
    (\alpha \hat{\theta}_{iR} + (1-\alpha) \hat{\theta}_{iT})) \|_2
    \leq B_L
  \end{equation*}
  for any $\alpha \in [0,1]$.
\end{asmp}

The differentiability condition in Assumption~\ref{asmp-3} is weak and
allows the loss function itself to be non-differentiable; for example,
absolute error and many asymmetric loss functions satisfy this
assumption.

Assumption~\ref{asmp-4} controls the growth of the test and training
samples.
\begin{asmp} \label{asmp-4} $P, R, Q \to\infty$ and $P^2/T \to 0$ as
  $T \to \infty$.
\end{asmp}

The requirements that $P$ and $R$ grow with $T$ are common. Parts of
the assumption are new, in particular the requirement that $P^2/T \to
0$.  See Lemma~\ref{res-convergence} for a discussion of its
implications.  In practical terms, this assumption requires that the
test sample be large and that the training sample be much larger, by
enough that including or excluding the test sample does not affect the
estimates of $\theta_1$ or $\theta_2$ very much.
